How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
added justification for the 10%

To examine the long method and the large class smells, we consider them in the context of Scratch as large script and large sprite smells respectively. For these two smells we use the number of blocks as the size metric. Figure \ref{fig:longmethod} presents the number of blocks in the scripts and the sprites of our dataset. We used these numbers to split the dataset and retrieve the top 10\% \todo{felienne, can we justify why 10 percent?} largest scripts and sprites, and in this way we found the thresholds to be used for the calculation of the large script and large sprite: it is 18 blocks and 59 blocks respectively. The results we obtained using these thresholds are presented in Section \ref{RQ3}.

@@

Also related to our research are works on code smells, initiated by the work by Fowler~\cite{fowler_refactoring:_1999}. His book gives an overview of code smells and corresponding refactorings. Fowler's work was followed by efforts focused on the automatic identification of code smells by means of metrics. Marinescu~\cite{marinescu_detecting_2001} for instance, uses metrics to identify \emph{suspect} classes: classes which could have design flaws. Alves \emph{et al.}~\cite{alves_deriving_2010} focus on a strategy to obtain thresholds for metrics from a benchmark Moha \emph{et al.}~\cite{moha_decor:_2010} designed the `DECOR' method which automatically generates a smell detection algorithms from specifications. The CCFinder tool~\cite{kamiya_ccfinder:_2002} finally, aims at detecting clones in source code, which are similar to our code duplication smell.

\section{Conclusions}
\label{sec:conclusion}
In this paper we presented a large scale study on \nAnalyzedPrograms projects we scraped from the Scratch repository. We analyzed these projects in terms of size, complexity, application of programming abstractions and utilization of programming concepts including procedures, variables, conditional statements, loops, and broadcast-receive functionality. We found that procedures and conditional loops are not commonly used. We further investigated the presence of code smells, including code duplication, dead code, long method and large class smells. Our findings indicate that Scratch programs suffer from code smells and especially dead code and code duplication.

>>>>

To examine the long method and the large class smells, we consider them in the context of Scratch as large script and large sprite smells respectively. For these two smells we use the number of blocks as the size metric. Figure \ref{fig:longmethod} presents the number of blocks in the scripts and the sprites of our dataset. We used these numbers to split the dataset and retrieve the top 10\% largest scripts and sprites, as is commonly done in both source code analysis~\cite{alves_deriving_2010} and analysis of end-user programming artefacts like spreadsheets~\cite{hermans2015detecting}. Using that strategy, we set the thresholds to be used for the calculation of the large script and large sprite: it is 18 blocks and 59 blocks respectively. The results we obtained using these thresholds are presented in Section \ref{RQ3}.

@@

%Also related to our research are works on code smells, initiated by the work by Fowler~\cite{fowler_refactoring:_1999}. His book gives an overview of code smells and corresponding refactorings. Fowler's work was followed by efforts focused on the automatic identification of code smells by means of metrics. Marinescu~\cite{marinescu_detecting_2001} for instance, uses metrics to identify \emph{suspect} classes: classes which could have design flaws. Alves \emph{et al.}~\cite{alves_deriving_2010} focus on a strategy to obtain thresholds for metrics from a benchmark Moha \emph{et al.}~\cite{moha_decor:_2010} designed the `DECOR' method which automatically generates a smell detection algorithms from specifications. The CCFinder tool~\cite{kamiya_ccfinder:_2002} finally, aims at detecting clones in source code, which are similar to our code duplication smell.

\section{Conclusions}
\label{sec:conclusion}
In this paper we presented a large scale study on \nAnalyzedPrograms~projects we scraped from the Scratch repository. We analyzed these projects in terms of size, complexity, application of programming abstractions and utilization of programming concepts including procedures, variables, conditional statements, loops, and broadcast-receive functionality. We found that procedures and conditional loops are not commonly used. We further investigated the presence of code smells, including code duplication, dead code, long method and large class smells. Our findings indicate that Scratch programs suffer from code smells and especially dead code and code duplication.
